\documentclass{beamer}
\usetheme{default}
\setbeamertemplate{blocks}[rounded][shadow=true]
\usepackage{listings}
\lstset{language=C++,
           basicstyle=\ttfamily,
           keywordstyle=\color{blue}\ttfamily,
           stringstyle=\color{red}\ttfamily,
           commentstyle=\color{green}\ttfamily
          }

%Footlines 
\usepackage{url} %for proper url entries
\useoutertheme{infolines}
\author{Sudev A C} 
\title{Bitcoin} 
\institute{NIT Calicut} 
%Titile Page 
\title[Computer Security]{Computer Security}
\subtitle[Browser Trojan]{Browser Trojan}
\author[John P Joseph]{John P Joseph}
\institute[NITC]{
  Department of Computer Science\\
  National Institute of Technology Calicut\\[1ex]
% \href{mailto:sudevdev@gmail.com}{sudevdev@gmail.com}
}
\date[November 2013]{November 13, 2013}

%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
\begin{document}



%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
\begin{frame}[plain]
  \titlepage
\end{frame}
%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
\begin{frame}{Lets start!}
\begin{Huge}
Browser Trojan \linebreak \linebreak
\end{Huge}

An extension modifies the interface and/or behaviour of a web browser.Many extensions has been downloaded and used by users to enhance browsing experience.
\end{frame}
%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$

\begin{frame}{Objective}
\begin{itemize}
\item To insert malicious code into a existing popular extension.
\item The malicious code should gain knowledge of users private data without his/her knowledge.
\item The knowledge attained should be transferred to a remote server.
\item If user attempts to disable the extension the malicious code should enable another extension of similar behaviour.
\end{itemize}

\end{frame}

%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$
%$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$

\begin{frame}{You don't believe us?}
\begin{itemize}
\item Fire your browser.
\item Login into to facebook account.
\item Act normal even if I write your password on the white board.
\end{itemize}
\end{frame}

\begin{frame}
Reference 
\begin{thebibliography}{99}

\bibitem{chdos}Original Paper by Satoshi Nakamoto\\ \begin{tiny}
  \url{http://bitcoin.org/bitcoin.pdf}
\end{tiny}

\bibitem{astimme}A good article\\ \begin{tiny}
 \url{http://www.investopedia.com/articles/investing/072913/how-bitcoin-works.asp}
\end{tiny}

\bibitem KKhan Academy Video Lecture\\ \begin{tiny}
  \url{https://www.khanacademy.org/economics-finance-domain/core-finance/money-and-banking/bitcoin/v/bitcoin-what-is-it}
\end{tiny}


\bibitem{astimme}Bitcoin Wiki\\ \begin{tiny}
 \url{https://en.bitcoin.it/wiki/Main_Page}
\end{tiny}


\bibitem{inode}Video clips\\ \begin{tiny}
 \url {http://www.youtube.com/watch?v=Um63OQz3bjo}\linebreak
 \url {http://www.youtube.com/watch?v=GmOzih6I1zs}
\end{tiny}
\bibitem{inode}Bitcoin real time analysis\\ \begin{tiny}
 \url {https://blockchain.info/}
\end{tiny}
\end{thebibliography}
\end{frame}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\begin{center}
\begin{huge}
thank you!
\end{huge}
\end{center}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
